\bf\mftitle

### 2011-02-16 doc/jInfer/autoeditor/autoeditor.tex
Documentation: AutoEditor.

\begin{itemize}
	\item API - API to display automaton in GUI.
	\item Base classes - Classes providing basic functionality that can be extended and combined to achieve desired visualization of an automaton.
	\item Derived classes - Classes derived from the base classes that are used in existing modules and simultaneously serve as examples.
	\item Layout factory - TODO
\end{itemize}

First, base classes and a creation of automaton visualization will be described.

@@

Trieda \code{Visualizer} dedi od JUNGoveho \code{VisualizationViewer}, takze poskytuje vsetky jeho metody a navyse podporu pre ulozenie automatu do obrazku - metody \code{saveImage()} a \code{getSupportedImageFormatNames()}. Pre ulozenie obrazku vsak tieto metody nie je nutne volat, pretoze AutoEditor GUI obsahuje tlacitko na ulozenie prave vykresleneho automatu do obrazku (viz dalej).

Constructor method bere ako argument instanciu triedy \code{Layout}. Viac informacii o tejto triede a jej pouzitie v kapitole TODO ref.

>>>>

\begin{itemize}
	\item API - API to display automaton in GUI.
	\item Base classes - Classes providing basic functionality that can be extended and combined to achieve desired visualization of an automaton.
	\item Derived classes - Classes derived from the base classes that are used in existing modules and simultaneously serve as examples.
	\item Layout creation - System of creating \code{Layout}s.
\end{itemize}

First, \code{Layout}s and use of base classes to create a visualization of automaton will be described.

\subsection{Layout}

\code{Layout} is a JUNG interface responsible primarily of representation of automaton and positions of its states. JUNG library provides several implementation of \code{Layout} interface. However, none of them is convenient for automatic automaton displaying, \jmodule{AutoEditor} provides two additional implementations. \code{Layout} by \emph{Julie Vyhnanovska}, used in her master thesis and \code{Layout} which is using external \emph{Graphviz} software. TODO odkazy v predchadzajucej vete.

Class providing creation of \code{Layout} instances is named \code{LayoutHelperFactory}.

\subsubsection{Vyhnanovska Layout}

As mentioned above, this Layout was implemented by \emph{Julie Vyhnanovska} as a part of her master thesis. TODO link? It positions automaton states to a square grid. This \code{Layout} gives good results for relatively small automata (about 10 states of less) but for larger ones, the results are quite disarranged and confused.

Source codes resides in package \code{cz.cuni.mff.ksi.jinfer.autoeditor.automatonvisualizer.layouts.vyhnanovska}.

\subsubsection{Graphviz Layout}

\code{Graphviz Layout} uses \emph{Graphviz}, third-party graph visualization software, to create positions of automaton states. TODO link? To use this \code{Layout}, \emph{Graphviz} has to be installed and path to \emph{dot} binary has to be set in options. This \code{Layout} gives nice results even on large automata.

Source codes resides in package \code{cz.cuni.mff.ksi.jinfer.autoeditor.automatonvisualizer.layouts.graphviz}.

\subsubsection{LayoutHelperFactory}

@@

\code {Visualizer} class extends JUNG \code{VisualizationViewer} class, so it provides all its methods and adds support for saving contained automaton to an image file. Responsible methods are \code{saveImage()} and \code{getSupportedImageFormatNames()}. However, to save an image of automaton it is not necessary to call this methods directly. \jmodule{AutoEditor} GUI contains button to save a save an image of displayed automaton. For information on how to to this, see TODO ref.

Constructor has one argument, instance of \code{Layout} class. \code{Layout} class is described in TODO ref.
